% -*- TeX-master: "main"; fill-column: 72 -*-

\section{Acknowledgments}
\label{acknowledgements}

Here we acknowledge those people and organizations that assisted in the development of version 0.3 release of the SBGNML specification. We acknowledge contributors that attended workshops and forum meetings or, in some other way, provided input to previous revisions to this effort. Then, we acknowledge the bodies that provided financial support for the development of the standard.

The following list includes members of the SBGN community that have contributed to the development of SBGNML in the past. Their efforts helped shape what SBGNML is today:
\begin{itemize}\setlength{\parskip}{-0.2ex}

\item Mirit I. Aladjem
\item Sarah E. Boyd
\item Emek Demir
\item Akira Funahashi
\item Hiroaki Kitano
\item Nicolas Le~Nov\`{e}re
\item Yukiko Matsuoka
\item Huaiyu Mi
\item Stuart L. Moodie
\item Herbert M. Sauro
\item Falk Schreiber
\item Anatoly Sorokin
\item Martijn P. van Iersel
\item Alice C. Vill\'eger

\end{itemize}

The UML diagrams were constructed using Visual Paradigm, a leading provider for Business and IT Transformation software solutions.

\section{Financial Support}

The development of SBGN was mainly supported by a grant from the Japanese \emph{New Energy and Industrial Technology Development Organization} (NEDO, \url{http://www.nedo.go.jp/}). The \emph{Okinawa Institute of Science and Technology} (OIST, \url{http://www.oist.jp/}), the \emph{AIST Computational Biology Research Center} (AIST CBRC, \url{http://www.cbrc.jp/index.eng.html}) the British \emph{Biotechnology and Biological Sciences Research Council} (BBSRC, \url{http://www.bbsrc.ac.uk/}) through a Japan Partnering Award, the European Media Laboratory (EML Research gGmbH, \url{http://www.eml-r.org/}), and the Beckman Institute at the California Institute of Technology (\url{http://bnmc.caltech.edu}) provided additional support for SBGN workshops. Some help was supplied by the \emph{Japan Science and Technology Agency} (JST, \url{http://www.jst.go.jp/}) and the \emph{Genome Network Project} of the Japanese Ministry of Education, Sports, Culture, Science, and Technology (MEXT, \url{http://www.mext.go.jp/}) for the development of the gene regulation network aspect of SBGN, and from the \emph{Engineering and Physical Sciences Research Council} (EPSRC, \url{http://www.epsrc.ac.uk}) during the redaction of the specification. The \emph{German Ministry of Education and Research} (\url{https://www.bmbf.de/}) provided support for an SBGN workshop, the redaction of the specification, and development of the SBGNML specification (de.NBI partner project ``ModSim'' (FKZ: 031L0104A)). Funding from \emph{National Institute of General Medical Sciences (NIGMS)} grant (P41 GM103504), \emph{National Human Genome Research Institute (NHGRI)} grant (U41 HG006623), and \emph{The Scientific and Technological Research Council of Turkey} grant (113E161) was additionally used for work on the specification. Funding from the US National Institutes of Health (NIH, grant number 2R01GM070923-13) supported software development related to SBGN.
